1.6: Optimize Workflow: Projects, Markdown, and Git

### 2019-09-13 content/class/06-class.Rmd
Updated slides and practice page for lesson 1.6

- [<i class="fas fa-external-link-square-alt"></i> Lecture Slides](/slides/05-slides.html)

@@

Today you will be working on [R practice problems](/r/05-r-practice.html). Check back later for solutions.

# Statistics and Software Survey

I have posted ["answers"](/homeworks/00-preliminary-survey-answers.html) to the statistics survey.

@@

Check back here!

>>>>

- [<i class="fas fa-external-link-square-alt"></i> Lecture Slides](/slides/06-slides.html)

@@

Today's "[practice problems](/r/06-r-practice.html)" are a series of raw `.Rmd` files that I've used for various things, so you can see how they work.

@@

See the last 2 slides and the readings page for my workflow, my suggestions to you, and a series of links to more resources and readings.

### 2019-09-13 content/r/06-r-practice.Rmd
Updated slides and practice page for lesson 1.6

---
title: "1.5 Data Wrangling with tidyverse - R Practice"
editor_options: 
  chunk_output_type: console
---

@@

- [<i class="fab fa-markdown"></i> Download R Practice 4 answers as  `.Rmd`](/r/04-r-practice-answers.Rmd)
- [<i class="fab fa-markdown"></i> See my `.Rmd` for today's slides on github](https://github.com/ryansafner/metricsF19/blob/master/static/slides/06-slides.Rmd)

Download these and look through the markdown to see how they make the webpages or slides. Note the slides are a bit advanced - I use a lot of formatting!

>>>>

---
title: "1.6 Optimize Workflow: Projects, Markdown, and Git - R Practice"
editor_options: 
  chunk_output_type: console
---

@@

There's currently no actual *practice* problems, but you should start taking a look at some actual `.Rmd` files to see how they work, if you are interested:

- [<i class="fas fa-external-link-square-alt"></i> Workflow R Project on GitHub](http://github.com/ryansafner/workflow)

Look at my `Workflow` R project on GitHub (first link). Also, see the 2nd-to-last slide in the slides (updated)! Follow the instructions to download and open the `.RProj` file on your computer (in RStudio). Look around the files (in the bottom-right panel), and open `Example_paper.Rmd` to see how you might write a paper in `R Markdown`.

If you are curious, below are two other examples. The first is the raw `.Rmd` file I wrote that created the (`html`) answer key for R practice 4 (on `ggplot2`). The second is the code for today's slides, written in [`Xaringan`](http://github.com/yihui/xaringan) (a special, `html`-based slides package), hosted on github. Note the slides are quite advanced - I use a lot of html and css formatting to make them pretty!

- [<i class="fab fa-markdown"></i> `04-r-practice-answers.Rmd`](/r/04-r-practice-answers.Rmd)
- [<i class="fab fa-markdown"></i> See my `.Rmd` for today's slides on github](https://github.com/ryansafner/metricsF19/blob/master/static/slides/06-slides.Rmd)

### 2019-09-13 static/slides/06-slides.Rmd
Updated slides and practice page for lesson 1.6

>>>>

# My Workflow (that I suggest to you)

1. Create a new repository on Github.
2. Start a New R Project in R Studio (link it to the github repository - [see guide](http://happygitwithr.com))
3. Create a logical file system ([see example](https://github.com/ryansafner/workflow)), such as:
```
project # folder on my computer (the new working directory)
|
|- Data/ # folder for data files 
|- Scripts/ # folder .R code
|- Bibliography/ # folder for .bib files
|- Figures/ # folder to plots and figures to
|- paper.Rmd # write document here
```
4. Write document in `paper.Rmd`, loading/saving files from/to various folders in project
5. Knit document to `pdf` or `html`.
6. Occasionally, `stage` and `commit` changes with a description, `push` to GitHub.
